---
title: "Lab 5 Assignment"
author: "brittneynelsen"
date: "2021-02-23"
output: github_document
---

## Instructions

> A. Load Packages

```{r}
library(tidyverse)
```

> A. Print Data

```{r}
iris
iris <- as_tibble(iris)
iris
```

> B. Rename each variable so that it is all lower-case and uses an underscore _ instead of a period . in the name (the recommended coding style in the tidyverse style guide). Print the resulting table.

```{r}
iris_r <- rename(
  iris, 
  sepal_length = Sepal.Length, 
  sepal_width = Sepal.Width, 
  petal_length = Petal.Length,
  petal_width = Petal.Width,
  species = Species
)

iris_r
```

> C. Convert the four numerical variables from mm to cm by multiplying by 10. Print the resulting table.

```{r}
iris_cm <- mutate(iris_r, sepal_length = sepal_length * 10,
       sepal_width = sepal_width * 10,
       petal_length = petal_length * 10,
       petal_width = petal_width * 10)

iris_cm
```

> D. Calculate sepal area and petal area (area is equal to length multiplied by width). Print a table with only the variables sepal area, petal area, and species.

```{r}
iris_area <- mutate(iris_cm, sepal_area = sepal_length * sepal_width, 
                    petal_area = petal_length * petal_width) %>%
  select(petal_area, sepal_area, species)
iris_area
```

> E. Calculate sepal area and petal area (area is equal to length multiplied by width). Print a table with only the variables sepal area, petal area, and species.
- sample size
- maximum value
- minimum value
- range
- median
- first quartile (q1)
- third quartile (q2)
- inter-quartile range (iqr)

```{r}
summarize(iris, sample_size = n(), 
          min = min(Sepal.Length), 
          max = max(Sepal.Length), 
          range = max(Sepal.Length) - min(Sepal.Length), 
          median = median(Sepal.Length),
          q1 = quantile(Sepal.Length, probs = 0.25), 
          q2 = quantile(Sepal.Length, probs = 0.75), IQR = IQR(Sepal.Length))
```

> F. Calculate the following statistics for each species from the petal width variable and print the resulting table:
- sample size
- mean
- standard deviation
- variance
- standard error of the mean
- approximate 95% confidence interval

```{r}
iris_sum <- 
  iris %>%
  group_by(Species) %>%
  summarize(
  mean = mean(Petal.Width),
  sample_size = n(),
  sd = sd(Petal.Width),
  var = var(Petal.Width),
  sem = mean(Petal.Width) / sqrt(sample_size),
  ci_upper = mean + 2 * sem,
  ci_lower = mean - 2 * sem
)
```

> G. Visualize the relationship between petal length and species using a strip plot.

```{r}
ggplot(data = iris) +
  geom_jitter(mapping = aes(x = Species, y = Petal.Width))
```

> H. Starting with the previous graph, add the mean and 95% confidence interval for each species

```{r}
ggplot(data = iris) +
  geom_jitter(mapping = aes(x = Species, y = Petal.Width)) +
  geom_crossbar(
    data = iris_sum,
    mapping = aes(
      x = Species,
      y = mean,
      ymax = ci_upper,
      ymin = ci_lower),
    color = "red"
  )
```

> I. Visualize the relationship between petal length, petal width, and species using a scatterplot. Map the two numerical variables to the x and y axes and map species to the color and shape aesthetics.

```{r}
ggplot(data = iris) +
  geom_point(mapping = aes(x = Petal.Length, y = Petal.Width))
ggplot(data = iris) +
  geom_point(mapping = aes(x = Petal.Length, y = Petal.Width, color = Species), alpha = 0.5)
```


## Session Info

Here is my session information:

```{r}
sessioninfo::session_info()
```





